### 2016-11-26 thesis/intro/intro.tex
finished draft for the hallmarks of cancer section of intro

\noindent

% TODO: do I really need tumour heterogeneity??
\subsubsection{Tumour heterogeneity}
\label{subsub:tumour_heterogeneity}

>>>>

\noindent
By utilising many, if not all, of these major cancer hallmarks, cancer cells are able to initiate growth, proliferate, invade, metastasise and eventually kill the host if untreated.
There is an evident need for an efficient way to monitor and treat cancer patients, and these Hallmarks of Cancers will prove to be the best target for effective treatments of cancer in the future.

% TODO: do I really need tumour heterogeneity??
\subsubsection{Tumour heterogeneity (?)}
\label{subsub:tumour_heterogeneity}

\subsubsection{Cancer stem cells (?)}
\label{ssub:cancer_stem_cells}
